A Comparison of Graph Processing Systems

### 2020-09-11 documentation/paper/sections/overview/galois.tex
more consistency and todos

%!TEX root=../../main.tex

@@

For graph analytics purposes a topology aware work stealing scheduler, a priority scheduler and a library of scalable data structures have been implemented. Galois includes applications for many graph analytics problems, among these are single-source shorthest-paths (sssp), breath-first-search (bfs) and pagerank. For most of these applications Galois offers several different algorithms to perform these analytics problems and many setting options like the amount of threads used or policies for splitting the graph. All of these applications can be executed in shared memory systems and, due to the Gluon integration, with a few modifications in a distributed environment.

>>>>

%!TEX root=../../main.tex
\todo{Rückmeldung 2 umsetzen}

@@

For graph analytics purposes a topology aware work stealing scheduler, a priority scheduler and a library of scalable data structures have been implemented. Galois includes applications for many graph analytics problems, among these are Single-Source Shorthest-Paths (SSSP), Breath-First Search (BFS) and PageRank (PR). For most of these applications Galois offers several different algorithms to perform these analytics problems and many setting options like the amount of threads used or policies for splitting the graph. All of these applications can be executed in shared memory systems and, due to the Gluon integration, with a few modifications in a distributed environment.
